---
title: "Hands–On Data Visualization with ggplot2"
description: |
  How to Create Engaging and Well–Designed Visualizations in R
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Overview

This is the home page for the Pearson–O'Reilly Live Training Session "Hands–On Data Visualization with ggplot2". All course materials will be posted on this site.

### Details

*Instructor:* [Dr Cédric Scherer](https://cedric-scherer.com/top/about)   
*Date:* September 3, 2021

### What You’ll Learn

- Load data into R and visualize it with the help of the powerful ggplot2 library.
- Customize your ggplot2 output as you like including theming, colors, annotations, and many more.
- Get to know useful extension libraries that will boost your workflow and improve your ggplot2 design.
- Use Rmarkdown notebooks to build reproducible reports.
- Get insights how to prepare and wrangle data with the popular tidyverse package collection.

### Who is the Training for

- **Anyone** interested in creating visually appealing charts with R and ggplot2—no matter if you have no or minimal experience with R.
- **Data scientists** aiming to use the powerful ggplot2 library in their workflow for exploration and communication.
- **Business managers** that aim to quickly gain data insights based on reproducible and elegantly formatted charts and reports.

---

# Prerequisites and Preparation

- **Familiarity with Rstudio** *(required)*
  * Video: [Chapter 2 of “R Programming for Statistics and Data Science”](https://learning.oreilly.com/videos/r-programming-for/9781789950298/) by 365 Careers 
  * Book: [Chapter 1 of “R for Data Science”](https://learning.oreilly.com/library/view/r-for-data/9781491910382/) by Hadley Wickham & Garrett Grolemund
- **Basic Knowledge of R** *(helpful but not required)*
  * Video: [Chapters 3, 4, and 7 of “R Programming for Statistics and Data Science”](https://learning.oreilly.com/videos/r-programming-for/9781789950298/) by 365 Careers 
  * Book: [Chapter 4–6 of “R for Data Science”](https://learning.oreilly.com/library/view/r-for-data/9781491910382/) by Hadley Wickham & Garrett Grolemund
- **Data Wrangling with the tidyverse** *(helpful but not required)*
  * Scenario: [“Format and Shape Your Data in R with the Tidyverse”](https://www.oreilly.com/scenarios/format-and-shape/9781492079064/) by Martin Frigaard 
  * Book: [Chapter 9–16 (Section: Wrangle) of “R for Data Science”](https://learning.oreilly.com/library/view/r-for-data/9781491910382/) by Hadley Wickham &  Garrett Grolemund

---

# Course Set-Up

To run any of the materials locally on your own machine, you will need the following:

- A recent version of R, [download from here.](https://cloud.r-project.org/)
- A recent version of RStudio, [download from here.](https://rstudio.com/products/rstudio/download/#download)
- The following R packages: [`tidyverse`](https://www.tidyverse.org/) (includes [`ggplot2`](https://ggplot2.tidyverse.org/)), [`ggrepel`](https://ggrepel.slowkow.com/), [`ggtext`](https://wilkelab.org/ggtext/), [`patchwork`](https://patchwork.data-imaginist.com/), [`ggforce`](https://ggforce.data-imaginist.com/), [`ragg`](https://ragg.r-lib.org/), [`magick`](https://docs.ropensci.org/magick/).  

You can install all required R packages at once by running the following code in the R command line

```{r install, eval=FALSE, echo=TRUE}
# Package names
packages <- c("tidyverse", "ggrepel", "ggtext", "patchwork", "ragg", "magick")

# Install packages that are not yet installed
if (any(packages %in% rownames(installed.packages()) == FALSE)) {
  install.packages(packages[!packages %in% rownames(installed.packages())])
}
```



## Reuse {.appendix}

<i>Text and figures are licensed under Creative Commons Attribution <a href='https://creativecommons.org/licenses/by/4.0/'>CC BY 4.0</a>.<br>Note that figures in slides may be pulled in from external sources and may be licensed under different terms.</i>
