---
title: "Hands–On Data Visualization with ggplot2"
description: "How to Create Engaging and Well–Designed Visualizations in R"
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Overview

This is the home page for the Pearson Live Training Session "Hands–On Data Visualization with ggplot2" for O'Reilly. All course materials will be posted on this site.

### Details

*Instructor:* [Dr Cédric Scherer](https://z3tt.github.io/hands-on-ggplot2/about.html)   
*Date:* April 19, 2022

### What You’ll Learn

- Load data into R and visualize it with the help of the powerful ggplot2 library.
- Customize your ggplot2 output as you like including theming, colors, annotations, and many more.
- Get to know useful extension libraries that will boost your workflow and improve your ggplot2 design.
- Use Rmarkdown notebooks to build reproducible reports.
- Get insights how to prepare and wrangle data with the popular tidyverse package collection.

### Who is the Training for

- **Anyone** interested in creating visually appealing charts with R and ggplot2—no matter if you have no or minimal experience with R.
- **Data scientists** aiming to use the powerful ggplot2 library in their workflow for exploration and communication.
- **Business managers** that aim to quickly gain data insights based on reproducible and elegantly formatted charts and reports.

---

# Course Set-Up

To run any of the materials locally on your own machine, you will need the following:

- A recent version of **R** (download from [here](https://cloud.r-project.org/)) and **RStudio**, (download from [here](https://rstudio.com/products/rstudio/download/#download)).
    * for more detailed instructions see [Chapter 2 of “R Programming for Statistics and Data Science”](https://learning.oreilly.com/videos/r-programming-for/9781789950298/) by 365 Careers
- The following R packages:
  + [`tidyverse`](https://www.tidyverse.org/) (includes [`ggplot2`](https://ggplot2.tidyverse.org/))
  + [`cowplot`](https://wilkelab.org/cowplot/index.html)
  + [`ggforce`](https://ggforce.data-imaginist.com/)
  + [`ggrepel`](https://ggrepel.slowkow.com/)
  + [`ggtext`](https://wilkelab.org/ggtext/)
  + [`magick`](https://docs.ropensci.org/magick/)
  + [`patchwork`](https://patchwork.data-imaginist.com/)
  + [`ragg`](https://ragg.r-lib.org/)
  + [`rnaturalearth`](https://docs.ropensci.org/rnaturalearth/)
  + [`sf`](https://r-spatial.github.io/sf/)

You can install all required R packages at once by running the following code in the R command line:

```{r install, eval=FALSE, echo=TRUE}
# Package names
packages <- c("tidyverse", "cowplot", "ggforce", "ggrepel", "ggtext", "magick", "patchwork", "ragg", "rnaturalearth", "sf")
install.packages(packages)
```

To run the code, open up Rstudio and copy–paste the code in **console window** and hit enter. Several messages should pop up. Scan these messages that are returned for errors and troubleshoot them if necessary. Warnings and other informational messages can be ignored.

---

# Prerequisites and Preparation

- **Familiarity with Rstudio** *(required)*<br><br>Suggested Material:
  * Book: [Chapter 1 of “R for Data Science”](https://learning.oreilly.com/library/view/r-for-data/9781491910382/) by Hadley Wickham & Garrett Grolemund
  * Video: [Chapter 2 of “R Programming for Statistics and Data Science”](https://learning.oreilly.com/videos/r-programming-for/9781789950298/) by 365 Careers 
    
- **Basic Knowledge of R** *(helpful but not required)*<br><br>Suggested Material:
  * Book: [Chapter 4–6 of “R for Data Science”](https://learning.oreilly.com/library/view/r-for-data/9781491910382/) by Hadley Wickham & Garrett Grolemund
  * Book: [Chapter 1–3 “R for Everyone: Advanced Analytics and Graphics, 2nd Edition”](https://learning.oreilly.com/library/view/r-for-everyone/9780134546988/) by Jared Lander 
  * Book: [Section 1 and 3 “Programming Skills for Data Science: Start Writing Code to Wrangle, Analyze, and Visualize Data with R”](https://learning.oreilly.com/library/view/programming-skills-for/9780135159071/) by Joel Ross & Michael Freeman
  * Video: [Chapters 3, 4, and 7 of “R Programming for Statistics and Data Science”](https://learning.oreilly.com/videos/r-programming-for/9781789950298/) by 365 Careers 

    
- **Data Wrangling with the tidyverse** *(helpful but not required)*<br><br>Suggested Material:
  * Book: [Chapter 9–16 (Section: Wrangle) of “R for Data Science”](https://learning.oreilly.com/library/view/r-for-data/9781491910382/) by Hadley Wickham &  Garrett Grolemund
  * Scenario: [“Format and Shape Your Data in R with the Tidyverse”](https://www.oreilly.com/scenarios/format-and-shape/9781492079064/) by Martin Frigaard 



## Reuse {.appendix}

<i>Text and figures are licensed under Creative Commons Attribution <a href='https://creativecommons.org/licenses/by/4.0/'>CC BY 4.0</a>.<br>Note that figures in slides may be pulled in from external sources and may be licensed under different terms.</i>
